A UK Case Study on\\Cybersecurity Education and Accreditation

### 2019-07-26 FIE2019-final.tex
Changes to Accreditation section, plus new case study section

%{\bf JHD to ? Poll CPHC, and/or survey job adverts.}
\section{Accreditation by PSRBs: {\emph{RQ3}}}

In the UK as in most jurisdictions, higher education provision addresses general computer science and specialist cybersecurity courses. A significant number of undergraduate and postgraduate programmes are available in both the areas of computer science and cybersecurity (and closely related fields computer security, digital/computer forensics, etc). In the UK, the Universities and Colleges Admissions Service (UCAS) lists over 40 higher education institutions providing undergraduate qualifications related to cybersecurity for entry in September 2019. An even larger number of institutions provide study opportunities related to more general computer science. UCAS lists 246 provides for undergraduate programmes related to computer science.

Accreditation has evolved to directly addresses the cybersecurity challenges in both general computer science programmes and specialist cybersecurity programmes. In the UK, accreditation in the broad computing area is being performed by a few different agencies. These include:

\textbf{1. Not-for-Profit Organisations}

Tech Partnership Degrees is a not-for-profit organisation that provides endorsements to higher education programmes with specific curricula elements aimed at job market requirements. One of the curricula elements is related to cybersecurity. Tech Partnership Degrees have a specialist scope, endorsing programmes in the area of IT Management for Business and Software Engineering for Business. Tech Partnership Degrees currently endorse 14 IT Management for Business Programmes and five Software Engineering for Business Programmes. As such, Tech Partnership Degrees currently have limited impact upon more general computer science education and none upon specialist cybersecurity education.

The Institute of Coding is a not-for-profit entity, led by the University of Bath, that intends to enhance how digital skills are developed in higher education in the UK~\cite{Davenportetal2019a}. This is likely to include cybersecurity related skills. Like the Tech Partnership, the focus is upon job market requirements. Additionally the Institute is looking at potentially endorsing the demonstrable capabilities of graduates as shown by their university studies, work experience and work placements. Given the size of this initiative this potentially has a significant role to play however at time of writing it is clearly a work in progress.

\textbf{2. National Cyber Security Centre (NCSC)}

The NCSC is a UK Government organisation tasked with enhancing the cybersecurity of the UK. The NCSC publishes and accredits to a number of cybersecurity standards~\cite{NCSC2017}. These standards are linked to the ACM recommendations for curricula \cite{ACM2013a}. To date the major focus of NCSC accreditation has been upon Masters degrees specialising in cybersecurity. More recently the NCSC has also began accrediting integrative masters programmes, undergraduate degrees in cybersecurity and computer science degrees with a significant cybersecurity focus \cite{NCSC2018b}.

Currently accredited are 15 cybersecurity MSc programmes with a further 11 provisional accredited, 3 integrated masters cybersecurity programmes and 1 cybersecurity Degree Programme with a further 2 provisionally accredited. Hence the extent of accreditation is currently reasonably limited in terms of reach to computer science programmes. This appears to be a positive initiative that will hopefully further develop over time.

\textbf{3. Professional Bodies/Learned Societies}

BCS, The Chartered Institute for IT (BCS) and the Institution of Engineering and Technology (IET) both accredit programmes in the general area of computer science and the more specialist area of cybersecurity discipline areas. The accreditation provided by these institutes are underpinned by international initiatives such as the Washington Accord\footnote{\url{http://www.ieagreements.org/accords/washington/}.} and the Seoul Accord\footnote{\url{https://www.seoulaccord.org/}.}. These memoranda support the internationalising of the curriculum and promote consistency and parity in computer science education globally.   These professional bodies are also registered charities and hence have responsibilities for public good which extends beyond short term job market needs \cite{Stensaker2006}, \cite{Mutereko2017}. Both the BCS and the IET have a long history of expecting coverage of environmental factors within the programmes they accredit. The BCS has for a number of years been expecting significant coverage of what it terms  {\emph{Legal, Ethical, Social and Professional Issues}}~\cite{Brooke2018}. Clearly cybersecurity has been and continues to be part of these expectations.

In recent years the BCS has evolved its accreditation practices to promote and mandate the inclusion of cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1}.
%\begin{center}
  \begin{table}[h!]
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - A. Developing Expectations &  \\ \hline
    UK Government Cybersecurity Strategy \cite{ukcyberstrategy:2016} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and  (ISC)$^2$ - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium (ISC)$^2$ \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - C. Accreditation - what progress has been made? &  \\ \hline
    All visited institutions expected to be fully compliant 
 (BCS follow a 5-year Accreditation Cycle)  & September 2020\\ \hline
  \end{tabular}
  \end{table}
%\end{center}

@@

Internationally the expectations regarding both the breadth and depth of the expected cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many governments, the UK Government has been actively been seeking ways to address this~\cite{UKCabinetOffice2014,ukcyberstrategy:2016}. In parallel to the work complete by the ACM~\cite{ACM2013a}, in the UK considerable effort was taken to ensure industry, higher education, government and the relevant professional bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society~\cite{Irons2016}. In 2013, an initiative was set up by (ISC)$^2$, CPHC (the representative body of UK computer science departments) and the UK Cabinet Office to examine embedding cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of cybersecurity education and proposed a framework for embedding these principles in UK computer science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate computer science degrees. This work initially lead to a white paper related to a proposal in the form of a white paper~\cite{CPHCISC2014}, followed by a set of guidelines~\cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that cybersecurity is included as a component of the BCS accreditation criteria, reflects the importance placed on cybersecurity and the expectation that all computing graduates should have knowledge and skills in cybersecurity as they move towards chartered status.

@@

The ambition of this approach is to influence the curricula of all programmes seeking accreditation (regardless of the precise discipline area.)  The approach taken is not intended to be prescriptive or stifle innovation, however it is intended to promote curricula that would benefit the students upon programmes, their future employers and wider society.  In this context this is realised as an expectation cybersecurity is an inclusion in all degrees accredited by the BCS. e.g. the expectation for coverage is true for computer science as well as cybersecurity programmes. Two criteria are expected to be covered by all programmes seeking accreditation. These are \cite{BCS2018a}:

{\emph{2.1.6 Recognise the legal, social, ethical and professional issues involved in the exploitation of computer technology and be guided by the adoption of appropriate professional, ethical and legal practices}}

{\emph{2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information system}}

Additionally programmes seeking Chartered Information Technology Professional (CITP) accreditation also have to cover:

{\emph{3.1.2 Knowledge and understanding of methods, techniques and tools for information modelling, management and security}}

@@

The BCS accreditation (criteria 2.1.6, 2.1.9 and 3.1.2) is not prescriptive, but encourages institutions to embed cybersecurity teaching across a range of subject areas in the computer science curriculum such as programming, software design, databases, networking, architecture. In addition there an expectation that there is significant coverage of cybersecurity principles and fundamentals -- either as a stand alone module or as a significant component(s) of other modules. This approach differs from the ACM approach, where the expectations are more explicit and the curriculum expectations are specified at a more granular level.

\subsection{What Are Universities Told?}
The agreed Cybersecurity Principles and Learning Outcome~\cite{CPHCISC2} were discussed with the wider education community by a road-show led by CPHC. A series of workshops took place in 2015 which presented the rationale for embedding cybersecurity in the curriculum of computer science degrees. The workshops included case studies from universities who had embedded cybersecurity into their computer science curricula illustrating different approaches to implementation. The workshops had 102 attendees from the academic computer science community representing 60 UK Universities.

The {\emph{BCS Guidelines on Course Accreditation}} are published online~\cite{BCS2018a}. The BCS also publishes the changes that have been made~\cite{BCS2018b}. When changes are made, the BCS communicates the changes by email and in writing to all the BCS Educational Affiliates, that is all the institutions that seek accreditation from the BCS. The expectations for cybersecurity were extended in the June 2015 version of the guidelines for consideration at accreditation visits that took place from September 2015 or later.

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature. Formally, the cycle is five years in duration. The new expectations have been implemented as follows. To ensure continuous accreditation, accreditation visits are normally scheduled every five years. At the time of the next visit in this accreditation cycle, accreditation is conditional upon an institution having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipated that from 2020 the expectation will be all accredited programmes have the new expectations fully embedded.

In the year prior to an accreditation visit, institutions are invited to a briefing from the BCS. The intention of the briefing is to help ensure accreditation visits are successful from the perspective of both the BCS and the institution. The briefings take place virtually. The briefing includes a summary of the process, discussion of recent changes, guidance regarding the application and a summary of common issues that are being seen in other institutions. Significant opportunity for seeking clarification is provided. One of the issues that is highlighted is not all institutions have yet evolved their programmes to fully address the increased expectation for cybersecurity. This is resulting in accreditation being contingent upon an institution taking action to address this short fall or in some cases the withdrawal of accreditation. A number of institutions are in the process of adjusting their curricula to meet the new expectations. In this case, the BCS notes the changes to programme design, the outputs from which will be scrutinised at the next accreditation visit.

@@

This initiative is a collective attempt to formally include cybersecurity in all BCS Accredited programmes. Some of these programmes will be specialist cybersecurity programmes, however the majority will take a different emphasis. This is a work in progress. A full cycle of accreditation visits has not yet taken place following the adjustment to the BCS Guidelines. What is being observed is the majority of visited institutions have now either adjusted their curricula to extend the coverage of cybersecurity or have a plan in place to do so. However, a minority are requiring encouragement to do so.

From the start of the Autumn 2015 term, up to and including the Autumn 2018 term, the BCS have carried out 70 accreditation visits (including four international visits). The BCS identified action was required to address concerns related to cybersecurity at 16 institutions. So 54 institutions were already delivering cybersecurity in keeping with the BCS expectations.

@@

Short terms 90 Day Responses where required from four institutions; the outcomes of these actions were as follows:

\begin{itemize}                                                                
\item Of the 11 UG programmes involved all were approved `{\emph{At Threshold}}';
\item Of the 9 UG programmes involved, 8 were approved and 1 refused;
\item Of the 5 UG programmes involved, all approved `{\emph{At Threshold}}';
\item Of the 3 UG programmes involved, all 3 were refused.
\end{itemize}

Good practice was identified at one university by the commendation:
 \begin{quote}
``{\emph{The second year project provides an opportunity for exploring security aspects in depth with an industrial use case.}}''
\end{quote}

In summary, this shows that many UK institutions have now embedded cybersecurity in their provision, a number are in the process of doing so and a minority have chosen not to. Clearly not all institutions in the UK necessarily have to apply for accreditation, or apply for accreditation for all their programmes, but even so this is significant evidence of inclusion of cybersecurity to an agreed standard.

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager at BCS, The Chartered Institute for IT for supplying the summary information related to accreditation of UK degree programmes. Many people, accreditors and accredited, have contributed to improving the standard of cybersecurity teaching in the UK, and spreading good practice.  All authors' institutions are members of the Institute of Coding (\url{https://instituteofcoding.org/}), an initiative funded by the Office for Students (England) and the Higher Education Funding Council for Wales.
\par
{\emph{N.B.}} The first two authors are current Vice-Presidents of BCS, The Chartered Institute for IT, and the third and fourth are past and present Chairs of the BCS Academic Accreditation Committee, providing significant personal insight into the UK's national accreditation policy and procedures.

>>>>

%{\bf JHD to ? Poll CPHC, and/or survey job adverts.}
\section{Accreditation by PSRBs ({\emph{RQ3}})}

In the UK --- as in most jurisdictions --- higher education provision addresses general computer science and specialist cybersecurity courses. A significant number of undergraduate and postgraduate programmes are available in both the areas of computer science and cybersecurity (and closely related fields, such as computer security, digital/computer forensics, etc). The UK's Universities and Colleges Admissions Service (UCAS) lists over 40 higher education institutions providing undergraduate qualifications related to cybersecurity for entry in September 2019. An even larger number of UK institutions provide study opportunities related to more general undergraduate computer science: UCAS lists 246 providers for undergraduate programmes for the 2019/2020 academic year.

Accreditation has evolved to directly addresses the cybersecurity challenges in both general computer science programmes and specialist cybersecurity programmes. In the UK, accreditation in the broad computing area is being performed by a few organisations with overlapping interests and priorities. These include:

\subsection{National Cyber Security Centre (NCSC)}

The NCSC is a UK Government organisation tasked with enhancing the cybersecurity of the UK. The NCSC publishes and accredits to a number of cybersecurity standards~\cite{NCSC2017}; these standards are linked to the ACM recommendations for curricula~\cite{ACM2013a}. To date, the major focus of NCSC accreditation has been upon Masters degrees specialising in cybersecurity. More recently the NCSC has also began accrediting integrative masters programmes, undergraduate degrees in cybersecurity, and computer science degrees with a significant cybersecurity focus.

The NCSC have accredited 15 cybersecurity MSc programmes with a further 11 provisional accredited, 3 integrated masters cybersecurity programmes and 1 cybersecurity degree programme, with a further 2 provisionally accredited. Hence the extent of accreditation is currently reasonably limited in terms of reach to computer science programmes. This appears to be a positive initiative that will further develop over the next few years, especially with increasing industry engagement in this area.

\subsection{Not-for-Profit Organisations}

Tech Partnership Degrees is a not-for-profit organisation that provides endorsements to higher education programmes with specific curricula elements aimed at job market requirements. One of the curricula elements is related to cybersecurity. Tech Partnership Degrees have a specialist scope, endorsing programmes in the named areas of ``IT Management for Business'' and ``Software Engineering for Business''. Tech Partnership Degrees currently endorse 14 IT Management for Business Programmes and five Software Engineering for Business Programmes. As such, Tech Partnership Degrees currently have limited impact upon more general computer science education and none upon specialist cybersecurity education.

The Institute of Coding\footnote{\url{https://instituteofcoding.org}} is a not-for-profit entity, led by the University of Bath, that intends to enhance how digital skills are developed in higher education in the UK~\cite{Davenportetal2019a}. This is likely to include cybersecurity related skills. Like the Tech Partnership, the focus is upon job market requirements. Additionally the Institute is looking at potentially endorsing the demonstrable capabilities of graduates as shown by their university studies, work experience and work placements. Given the size of this initiative this potentially has a significant role to play however at time of writing it is clearly a work in progress.

\subsection{Professional Bodies and Learned Societies}

Both BCS, The Chartered Institute for IT (BCS) and the Institution of Engineering and Technology (IET) accredit programmes in the general area of computer science and the more specialist area of cybersecurity discipline areas. The accreditation provided by these institutes are underpinned by international initiatives such as the Washington Accord\footnote{\url{http://www.ieagreements.org/accords/washington/}.} and the Seoul Accord\footnote{\url{https://www.seoulaccord.org/}.}. These memoranda support the internationalising of the curriculum and promote consistency and parity in computer science education globally.  These professional bodies are also UK charities and hence have responsibilities for public good which extends beyond short term job market needs~\cite{Stensaker2006,Mutereko2017}. Both the BCS and the IET have a long history of expecting coverage of environmental factors within the programmes they accredit. The BCS has for a number of years been expecting significant coverage of what it terms  {\emph{Legal, Social, Ethical and Professional Issues}}~\cite{Brooke2018}. Clearly cybersecurity has been and continues to be part of these expectations.

\section{Case Study: BCS Accreditation}

In recent years the BCS has evolved its accreditation practices to promote and mandate the inclusion of cybersecurity within the programmes the body accredits. The timeline which this process has followed in presented in Table~\ref{table:1}, and will be discussed in more detail in the following case study.

%\begin{center}
  \begin{table}[h!]
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - A. Developing Expectations &  \\ \hline
    UK Government Cybersecurity Strategy \cite{ukcyberstrategy:2016} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies -- led by CPHC and  (ISC)$^2$ -- leading to the development of cybersecurity learning guidelines to be embedded into BCS accredited UK computer science and IT-related degrees~\cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium (ISC)$^2$ \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION ({\emph{RQ3}}) - C. Accreditation - what progress has been made? &  \\ \hline
    All visited institutions expected to be fully compliant 
 (BCS follow a five-year accreditation cycle)  & September 2020\\ \hline
  \end{tabular}
  \end{table}
%\end{center}

@@

Internationally the expectations regarding both the breadth and depth of the expected cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many governments, the UK Government has actively been seeking ways to address this~\cite{UKCabinetOffice2014,ukcyberstrategy:2016}. In parallel to the work completed by the ACM~\cite{ACM2013a} in the USA, considerable effort in the UK have been taken to ensure industry, higher education, government and the relevant professional bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society~\cite{Irons2016}. In 2013, an initiative was set up by (ISC)$^2$, CPHC (the representative body of UK computer science departments) and the UK Cabinet Office to examine embedding cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of cybersecurity education and proposed a framework for embedding these principles in UK computer science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 universities that offer undergraduate computer science degrees. This work initially lead to a white paper related to a proposal in the form of a white paper in 2014~\cite{CPHCISC2014}, followed by a set of guidelines in 2015~\cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that cybersecurity is included as a component of the BCS accreditation criteria reflects the importance placed on cybersecurity and the expectation that all computing graduates should have knowledge and skills in cybersecurity as they move towards chartered status.

@@

The ambition of this approach was to influence the curricula of all programmes seeking accreditation (regardless of the precise discipline area); it was not intended to be prescriptive or stifle innovation, however it is intended to promote curricula that would benefit the students upon programmes, their future employers and wider society.  In this context this is realised as an expectation cybersecurity is an inclusion in all degrees accredited by the BCS. e.g. the expectation for coverage is true for computer science as well as cybersecurity programmes. Two criteria are expected to be covered by all programmes seeking accreditation. These are:

``{\emph{2.1.6 Recognise the legal, social, ethical and professional issues involved in the exploitation of computer technology and be guided by the adoption of appropriate professional, ethical and legal practices}}''

``{\emph{2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information system}}''~\cite{BCS2018a}

Additionally, programmes seeking Chartered Information Technology Professional (CITP) accreditation also have to cover:

``{\emph{3.1.2 Knowledge and understanding of methods, techniques and tools for information modelling, management and security}}''~\cite{BCS2018a}

@@

The relevant BCS accreditation (criteria 2.1.6, 2.1.9 and 3.1.2, as presented above) is not prescriptive, but encourages institutions to embed cybersecurity teaching across a range of subject areas in the computer science curriculum such as programming, software design, databases, networking, architecture. In addition there an expectation that there is significant coverage of cybersecurity principles and fundamentals -- either as a stand alone module or as a significant component(s) of other modules. This approach differs from the ACM approach~\cite{ACM2013a}, where the expectations are more explicit and the curriculum expectations are specified at a more granular level.

\subsection{What Are Universities Told?}

The agreed {\emph{Cybersecurity Principles and Learning Outcomes}}~\cite{CPHCISC2} were discussed with the wider education community, led by CPHC. A series of workshops took place in 2015 which presented the rationale for embedding cybersecurity in the curriculum of computer science degrees. The workshops included case studies from universities who had embedded cybersecurity into their computer science curricula illustrating different approaches to implementation. The workshops had 102 attendees from the academic computer science community representing 60 UK Universities.

The {\emph{BCS Guidelines on Course Accreditation}} are published online~\cite{BCS2018a}, with the BCS publishing any changes that have been made~\cite{BCS2018b}. When changes are made, the BCS communicates the changes by email and in writing to all the BCS Educational Affiliates, that is all the institutions that seek accreditation from the BCS. The expectations for cybersecurity were extended in the June 2015 version of the guidelines for consideration at accreditation visits that took place from September 2015 or later.

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature; formally, the cycle is five years in duration. The new expectations have been implemented as follows: to ensure continuous accreditation, accreditation visits are normally scheduled every five years; at the time of the next visit in this accreditation cycle, accreditation is conditional upon an institution having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipated that from 2020 the expectation will be all accredited programmes have the new expectations fully embedded.

In the year prior to an accreditation visit, institutions are invited to a briefing from the BCS. The intention of the briefing is to help ensure accreditation visits are successful from the perspective of both the BCS and the institution. The briefings take place virtually and includes a summary of the process, discussion of recent changes, guidance regarding the application and a summary of common issues that are being seen in other institutions. Significant opportunity for seeking clarification is provided. One of the issues often highlighted is that not all institutions have yet evolved their programmes to fully address the increased expectation for cybersecurity. This is resulting in accreditation being contingent upon an institution taking action to address this short fall or in some cases the withdrawal of accreditation. A number of institutions are in the process of adjusting their curricula to meet the new expectations. In this case, the BCS notes the changes to programme design, the outputs from which will be scrutinised at the next accreditation visit.

@@

This initiative is a collective attempt to formally include cybersecurity in all BCS Accredited programmes. Some of these programmes will be specialist cybersecurity programmes, however the majority will take a different emphasis; this is a work in progress. A full cycle of accreditation visits has not yet taken place following the adjustment to the BCS Guidelines~\cite{BCS2018b}. What is being observed is the majority of visited institutions have now either adjusted their curricula to extend the coverage of cybersecurity or have a plan in place to do so. However, a minority are requiring encouragement to do so.

From the start of the Autumn 2015 term, up to and including the Autumn 2018 term, the BCS have carried out 70 accreditation visits (including four international visits). The BCS identified action was required to address concerns related to cybersecurity at 16 institutions; thus, 54 institutions were already delivering cybersecurity in keeping with the BCS expectations.

@@

Short terms 90 Day Responses where required from four institutions; the outcomes of these actions were as follows: ({\emph{i}}) of the 11 UG programmes involved all were approved `{\emph{At Threshold}}'; ({\emph{ii}}) of the nine UG programmes involved, eight were approved and one refused; ({\emph{iii}}) of the five UG programmes involved, all approved `{\emph{At Threshold}}'; and ({\emph{iv}}) of the 3 UG programmes involved, all 3 were refused.

% \begin{itemize}                                                                
% \item Of the 11 UG programmes involved all were approved `{\emph{At Threshold}}';
% \item Of the 9 UG programmes involved, 8 were approved and 1 refused;
% \item Of the 5 UG programmes involved, all approved `{\emph{At Threshold}}';
% \item Of the 3 UG programmes involved, all 3 were refused.
% \end{itemize}

Good practice was identified at one university by the commendation:

 \begin{quote}
``{\emph{The second year project provides an opportunity for exploring security aspects in depth with an industrial use case.}}''
\end{quote}

In summary, this shows that many UK institutions have now embedded cybersecurity in their provision, a number are in the process of doing so and a minority have chosen not to. Clearly not all institutions in the UK necessarily have to apply for PSRB accreditation, or apply for accreditation for all their programmes, but even so this is significant evidence of inclusion of cybersecurity to an agreed standard.

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager at BCS, The Chartered Institute for IT for supplying the summary information related to accreditation of UK degree programmes. Many people, accreditors and accredited, have contributed to improving the standard of cybersecurity teaching in the UK, and spreading good practice.  All authors' institutions are members of the Institute of Coding, an initiative funded by the Office for Students (England) and the Higher Education Funding Council for Wales.
\par
{\emph{N.B.}} The first two authors are current Vice-Presidents of BCS, The Chartered Institute for IT, and the third and fourth are past and present Chairs of the BCS Academic Accreditation Committee, providing significant personal insight into the UK's national accreditation policy and procedures.
